---
author: ""
date: ""
title: "Analysis"
output:
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: flatly
    highlight: pygments
---

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(
  echo = TRUE,
  # include = FALSE,
  # cache = TRUE,
  # results = "markdown",
  # results = "hide",
  # fig.align = "center",
  # fig.show = "asis",
  fig.width = 10,
  fig.height = 10,
  # out.width = 6,
  # out.height = 6,
  warning = FALSE,
  message = FALSE
)

string_id <- "team"
string_id_plural <- "teams"
```


```{r packages, include = FALSE}
library("dplyr")
library("rlang")
library("tetext") # Personal package.
library("tedata") # Personal package.
```

```{r setup_funcs, include = FALSE}
pull_distinctly <- function(data = NULL, col = NULL) {
  col <- enquo(col)
  data %>%
    distinct(!!col) %>%
    arrange(!!col) %>%
    pull(!!col)
}
```


```{r import_data, include = FALSE}
path_data_raw <- file.path("data", "nba-tms-2018-03-04.rds")
data_raw <- readRDS(path_data_raw)
```

```{r data_supp, include = FALSE}
data_supp <-
  tedata::nba_tms_colors %>% 
  rename(screen_name = twitter_screen_name) %>%
  mutate(screen_name = tolower(screen_name)) %>% 
  select(tm, conference, division, screen_name, color = teamcolors_primary)

data <-
  data_raw %>% 
  mutate(screen_name = tolower(screen_name)) %>% 
  inner_join(data_supp, by = c("screen_name")) %>% 
  select(id = tm, color, everything())

data %>%
  count(id, screen_name, sort = TRUE)
```

```{r setup_vars, include = FALSE}
# ids <- data %>% pull_distinctly(id)
# colors_filt <- data %>% pull_distinctly(color)
ids <- data_supp_select %>% pull(id)
colors_filt <- data_supp_select %>% pull(color)

# ids_filt <- c("SAS", "GSW", "HOU", "CLE", "LAL", "SAC")
# ids_filt <- ids
ids_filt <-
  data_supp %>%
  # filter(conference %in% "Western") %>% 
  pull(tm)

idxs_filt <- match(ids_filt, ids)
colors_filt <- colors_filt[idxs_filt]
names(colors_filt) <- ids_filt

ids_filt_by2 <-
  data_supp %>%
  filter(division %in% "Southwest") %>% 
  pull(tm)

idxs_filt_by2 <- match(ids_filt_by2, ids)
colors_filt_by2 <- colors_filt[idxs_filt_by2]
names(colors_filt_by2) <- ids_filt_by2

id_filt_long <- "San Antonio Spurs"
id_filt <- "SAS"
idx_filt <- match(id_filt, ids)
color_filt <- colors_filt[idx_filt]

color_filt_inv <- temisc::get_color_hex_inverse(color_filt)
colors_filt_dual <- c(color_filt, color_filt_inv)
lab_other <- paste0("Not ", id_filt)
names(colors_filt_dual) <- c(id_filt, lab_other)
```

```{r data_facet_trim, include = FALSE}
data_facet <-
  data %>%
  filter(id %in% ids_filt) %>%
  # mutate(id = factor(id, levels = ids_filt)) %>% 
  clean_tweets(facet = id)

id_cnts <-
  data_facet %>%
  count(id, sort = TRUE)
id_cnts_top <- id_cnts %>% slice(1) %>% pull(id)
id_cnts_top_cnt <- id_cnts %>% slice(1) %>% pull(n)
id_cnts_bot <- id_cnts %>% slice(nrow(.)) %>% pull(id)
id_cnts_bot_cnt <- id_cnts %>% slice(nrow(.)) %>% pull(n)

data_facet_timefilter <-
  data_facet %>%
  compute_timefilter_facet(
    timebin = timestamp,
    facet = id
  )

data_facet_trim <-
  data_facet %>%
  trim_bytime(
    timebin = timestamp,
    start = data_facet_timefilter$date_start,
    end = data_facet_timefilter$date_end
  )

timestamp_min <- min(data_facet$timestamp)
timestamp_max <- max(data_facet$timestamp)

timestamp_last_start <- data_facet_timefilter$date_start
timestamp_first_end <- data_facet_timefilter$date_start
```

### About

This storyboard investigates the tweets from the official Twitter accounts
for each NBA Western Conference team. (Abbreviations of team names are used in visualizations.)
Where analysis of a single team is performed, 
the content of the `r id_filt_long` (`r id_filt`) account is used.

### __Temporal Count:__ From when did the extracted data come?

```{r viz_time_facet_all, echo = FALSE}
viz_time_facet_all <-
  data_facet_trim %>%
  visualize_time_facet(
    timebin = timestamp,
    color = id,
    facet = id,
    scale_manual_params = list(values = colors_filt, breaks = NULL),
    facet_params = list(scales = "fixed", ncol = NULL, nrow = NULL),
    theme_params = list(axis.text = ggplot2::element_text(size = ggplot2::rel(0.5))),
    labs_params = list(title = NULL)
  )
viz_time_facet_all
```

***

The first tweet shown is at
`r timestamp_last_start`, and the last tweet shown is at `r timestamp_first_end`.
The `r string_id` with the most tweets during this time is
`r id_cnts_top` (`r id_cnts_top_cnt`).
The `r string_id` with the least is
`r id_cnts_bot` (`r id_cnts_bot_cnt`).

_NOTE:_
Only tweets occuring between the last "first" tweet 
and the first "last" tweet across all entities are shown.
In reality, some timelines have tweets going back farther
and/or occurring more recently in time.
(The actual first tweet occurs at `r timestamp_min`, and the actual
last tweet occurs at `r timestamp_max`.) Nonetheless, tweets are truncated
across entities in order to "normalize" the data.


### __Temporal Count:__ Which hours of the day are the most common for each `r string_id`?


```{r viz_time_facet_hh, echo = FALSE}
viz_time_facet_hh <-
  data_facet_trim %>%
  mutate(hh = lubridate::hour(timestamp)) %>% 
  visualize_time_facet(
    timebin = hh,
    color = id,
    facet = id,
    scale_manual_params = list(values = colors_filt),
    facet_params = list(scales = "fixed", ncol = NULL, nrow = NULL),
    theme_params = list(axis.text = ggplot2::element_text(size = ggplot2::rel(0.5))),
    labs_params = list(title = NULL)
  )
viz_time_facet_hh
```

```{r viz_time_facet_hh_2, include = FALSE, eval = FALSE}
viz_time_facet_hh_2 <-
  data_facet_trim %>% 
  visualize_time_hh(
    timebin = time,
    color = id,
    facet = id,
    scale_manual_params = list(values = colors_filt),
    labs_params = list(title = NULL)
  )
viz_time_facet_hh_2

```

***

Most activity occurs at the end of the day. This makes sense--nearly all NBA games 
occur at night.

```{r add_tweet_kind_cols, include = FALSE}
data_facet_trim_kind <-
  data_facet_trim %>%
  add_tweet_kind_cols()
```

```{r tidify, include = FALSE}
rgx_tidiers <-
  get_tweet_rgx_tidiers()

unigrams <-
  data_facet_trim_kind %>%
  mutate(text = rtweet::plain_tweets(text)) %>%
  tidify_to_unigrams(
    text = text,
    rgx_unnest = rgx_tidiers$rgx_unnest,
    rgx_pattern = rgx_tidiers$rgx_pattern,
    rgx_replacement = "",
    rgx_ignore_custom = rgx_tidiers$rgx_ignore_custom
  )

bigrams <-
  data_facet_trim_kind %>%
  mutate(text = rtweet::plain_tweets(text)) %>%
  tidify_to_bigrams(
    text = text,
    rgx_pattern = rgx_tidiers$rgx_pattern,
    rgx_replacement = "",
    rgx_ignore_custom = rgx_tidiers$rgx_ignore_custom
  )

```

### __Word (Single) Frequency:__ What are the most common words for each `r string_id`?


```{r viz_unigram_cnts_facet, echo = FALSE}
viz_unigram_cnts_facet <-
  unigrams %>%
  visualize_cnts_facet(
    token = word,
    facet = id,
    color = id,
    num_top = 5,
    scale_manual_params = list(values = colors_filt),
    theme_params = list(axis.text = ggplot2::element_text(size = ggplot2::rel(0.5))),
    labs_params = list(title = NULL)
  )
viz_unigram_cnts_facet
```

***

It's evident that team accounts reference themselves a lot. (After all,
these accounts are used primarily for promotional purposes.)
Aside from team-level references, the team accounts mention
team players a lot, which is not suprising.

### __Word (Single) Frequency:__ What are the most common words for each `r string_id`?  (wordcloud)

```{r viz_unigram_cnts_wordcloud_facet, echo = FALSE}
ncol <- ceiling(sqrt(length(ids_filt_by2)))
nrow <- floor(sqrt(length(ids_filt_by2)))

par(mfrow = c(nrow, ncol))
invisible(
  purrr::map2(
    ids_filt_by2,
    colors_filt_by2,
    ~ visualize_cnts_wordcloud_facet(
      data = unigrams,
      token = word,
      facet = id,
      value_facet = .x,
      wordcloud_params = list(colors = .y, max.words = 25)
    )
  )
)
par(mfrow = c(1, 1))
```

***

_NOTE:_ Due to graphics limitations, only the subset of chosen `r string_id_plural` is shown.

### __Word (Pairs) Frequency:__ What are the most common pairs of words for each `r string_id`?

```{r bigram_freqs, include = FALSE}
bigram_freqs <-
  bigrams %>%
  compute_freqs_facet(
    token = word,
    facet = id
  )
bigram_freqs

bigram_freqs %>%
  dplyr::group_by(id) %>%
  dplyr::do(head(., 2))
```

```{r viz_bigram_freqs, echo = FALSE}
viz_bigram_freqs <-
  bigrams %>%
  visualize_bigram_freqs(
    token = word,
    facet = id,
    color = id,
    num_top = 1,
    scale_manual_params = list(values = colors_filt),
    theme_params = list(axis.text = ggplot2::element_text(size = ggplot2::rel(0.75))),
    labs_params = list(title = NULL)
  )
viz_bigram_freqs
```

***

Player names are more prominent here.

```{r unigram_sent_summ_facet, include = FALSE, eval = FALSE}
unigram_sent_summ_facet <-
  unigrams %>%
  compute_sent_summ_facet(
    token = word,
    feature = status_id,
    facet = id
  )
unigram_sent_summ_facet
```


```{r unigram_sentratios_facet_by2, include = FALSE, eval = FALSE}
unigram_sentratios_facet_by2 <-
  unigrams %>%
  filter(id %in% ids_filt_by2) %>% 
  compute_sentratios_facet_by2(
    token = word,
    facet = id
  )
unigram_sentratios_facet_by2

unigram_sentratios %>%
  dplyr::group_by(name_xy, sentiment) %>%
  dplyr::do(head(., 2))
```

```{r unigram_freqs_facet, include = FALSE, eval = FALSE}
unigram_freqs_facet <-
  unigrams %>%
  compute_freqs_facet(
    token = word,
    facet = id
  )
unigram_freqs_facet
```

```{r unigram_freqs_facet_by2, include = FALSE, eval = FALSE}
unigram_freqs_facet_by2 <-
  unigrams %>%
  filter(id %in% ids_filt_by2) %>% 
  compute_freqs_facet_by2(
    token = word,
    facet = id
  )
unigram_freqs_facet_by2
```

### __Word (Single) Frequency:__ What are the most common words, relative to `r id_filt`?

```{r viz_unigram_freqs_facet_by2, echo = FALSE}
viz_unigram_freqs_facet_by2 <-
  unigrams %>%
  filter(id %in% ids_filt_by2) %>% 
  visualize_freqs_facet_by2(
    token = word,
    facet = id,
    filter_facet = TRUE,
    facet_main = id_filt,
    labs_params = list(title = NULL)
  )
viz_unigram_freqs_facet_by2
```

***

Some commentary...

```{r unigram_logratios_facet_by2, include = FALSE, eval = FALSE}
unigram_logratios_facet_by2 <-
  unigrams %>%
  filter(id %in% ids_filt_by2) %>% 
  compute_logratios_facet_by2(
    token = word,
    facet = id,
    cnt_min = 50
  )
unigram_logratios_facet_by2
```

### __Word (Single) Log-Ratio Differences:__ How differnet is the word, relative to `r id_filt`?


```{r viz_unigram_logratios_facet_by2, echo = FALSE}
viz_unigram_logratios_facet_by2 <-
  unigrams %>%
  filter(id %in% ids_filt_by2) %>% 
  visualize_logratios_facet_by2(
    token = word,
    facet = id,
    filter_facet = TRUE,
    facet_main = id_filt,
    num_top = 3,
    # lab_other = lab_other,
    color_main = color_filt,
    # scale_manual_params = list(values = colors_filt_dual),
    labs_params = list(title = NULL)
  )
viz_unigram_logratios_facet_by2
```

***

### __Word (Single) Sentiment Differences:__ How different is each `r string_id`'s tone, relative to `r id_filt`?

```{r viz_unigram_sentratios_facet_by2, echo = FALSE, eval = FALSE}
viz_unigram_sentratios_facet_by2 <-
  unigrams %>%
  filter(id %in% ids_filt_by2) %>% 
  visualize_sentratios_facet_by2(
    token = word,
    facet = id,
    filter_facet = TRUE,
    facet_main = id_filt,
    filter_sent = TRUE,
    sent_main = "positive",
    num_top = 3,
    # lab_other = lab_other,
    color_main = color_filt,
    # scale_manual_params = list(values = colors_filt_dual),
    labs_params = list(title = NULL)
  )
viz_unigram_sentratios_facet_by2
```


```{r viz_unigram_sentratios_facet_by2_list, echo = FALSE}
sents_filt <- c("positive", "negative")
viz_unigram_sentratios_facet_by2_list <-
  sents_filt,
purrr::map(
  ~visualize_sentratios_facet_by2(
    data =unigrams %>% filter(id %in% ids_filt_by2)
    token = word,
    facet = id,
    filter_facet = TRUE,
    facet_main = id_filt,
    filter_sent = TRUE,
    sent_main = .x,
    num_top = 3,
    # lab_other = lab_other,
    color_main = color_filt,
    # scale_manual_params = list(values = colors_filt_dual),s
    labs_params = list(title = NULL, subtitle = .x)
  )
)
viz_unigram_sentratios_facet_by2_list
```
 
 ***

Some commentary...


  
